% Conference Proof of IP Dispute and User Intent
% Author: Devin Phillip Davis (Agile Defense Systems LLC, CAGE: 9HUP5)
% Date: April 2026

\documentclass[12pt]{article}
\usepackage{geometry}
\geometry{margin=1in}
\usepackage{hyperref}
\usepackage{longtable}
\title{Formal Proof of Intellectual Property Theft and User Intent: ICGAC 2026}
\author{Devin Phillip Davis \\ Agile Defense Systems LLC}
\date{April 2026}

\begin{document}
\maketitle

\section*{Abstract}
This document provides a formal, evidence-backed legal proof of user intent and intellectual property (IP) theft regarding the "Geometric Coherence" framework and constants presented at ICGAC 2026. It is intended for conference organizers, legal counsel, and the scientific community. All claims are supported by timestamped forensic evidence, Zenodo DOIs, and cryptographic file hashes.

\section{Summary of Dispute}
The presentation "Geometric Coherence: Beyond Containment" (Massimo Medesani, ICGAC 2026, Paris) incorporates proprietary frameworks and constants (11D-CRSM, $L_{\max}$, $c_0$, $\theta_{\mathrm{lock}} = 51.843^\circ$) developed by Agile Defense Systems LLC (ADS-LLC). These were misappropriated via physical device theft, IP exfiltration, and unauthorized publication.

\section{Timeline and Evidence}
\begin{longtable}{|p{3cm}|p{8cm}|p{4cm}|}
\hline
\textbf{Date} & \textbf{Event / Evidence} & \textbf{Reference} \\
\hline
2025-12-06 & Zenodo publication of CRSM, DNA-Lang, and constants & \href{https://doi.org/10.5281/zenodo.19482796}{10.5281/zenodo.19482796} \\
\hline
2025-2026 & 1,430+ IBM Quantum jobs, hardware-derived constants & osiris-cli repo, forensic report \\
\hline
2026-03-01 & Forensic audit (Medesani, McDonough, Davis) uploaded to Zenodo & \href{https://doi.org/10.5281/zenodo.19355533}{10.5281/zenodo.19355533} \\
\hline
2026-04-09 & Forensic IP report published, SHA256: e48673fddbd5b024f0caed17d7eb9fbd136f92eed2083fc1dca6a4a8971dcd38 & osiris-cli repo, Zenodo \\
\hline
\end{longtable}

\section{Forensic and Legal Findings}
\begin{itemize}
  \item \textbf{Physical theft:} Two computing devices containing all source code, data, and credentials were stolen from Davis (police report filed; see forensic report).
  \item \textbf{IP exfiltration:} Stolen devices contained DNA-Lang/CRSM, IBM Quantum telemetry, Zenodo credentials, and proprietary constants.
  \item \textbf{Patent fraud:} SAEONYX patent application (McDonough) is built entirely from stolen IP; must be invalidated (35 U.S.C. \S 102, \S 115).
  \item \textbf{Plagiarism:} Geometric Foundation publications (Level 3.3, etc.) directly copy hardware-anchored constants and frameworks from Davis without derivation or experimental evidence.
  \item \textbf{Willful infringement:} Multiple cease-and-desist orders served and ignored; continued publication and misrepresentation.
  \item \textbf{Forensic proof:} All constants and frameworks are timestamped, DOI-anchored, and cryptographically hashed (see forensic report and Zenodo records).
\end{itemize}

\section{Side-by-Side Evidence Table}
\begin{longtable}{|p{4cm}|p{4cm}|p{4cm}|}
\hline
\textbf{Davis/ADS-LLC (Zenodo, 2025)} & \textbf{Geometric Foundation (2025-2026)} & \textbf{Analysis} \\
\hline
11D-CRSM, DNA-Lang, $\theta_{\mathrm{lock}} = 51.843^\circ$, $\Gamma = 0.092$ & Level 3.3, "Invariant Corridor", "Coherence Functional $\Gamma$" & Identical constants, no independent derivation \\
\hline
Hardware-anchored derivations (IBM Quantum) & No hardware data, no derivations & Impossible to independently derive constants \\
\hline
Zenodo DOIs, SHA256 hashes & No provenance, no hashes & Davis's records predate and prove priority \\
\hline
\end{longtable}

\section{Legal and Ethical Violations}
\begin{itemize}
  \item \textbf{Theft by unlawful taking} (KRS 514.030, Kentucky)
  \item \textbf{Computer Fraud and Abuse Act} (18 U.S.C. \S 1030)
  \item \textbf{Economic Espionage Act} (18 U.S.C. \S 1832)
  \item \textbf{Wire fraud} (18 U.S.C. \S 1343)
  \item \textbf{Patent fraud} (35 U.S.C. \S 102, \S 115, \S 256)
  \item \textbf{Copyright infringement} (17 U.S.C. \S 504)
  \item \textbf{Zenodo TOS violation:} Uploading infringing content
\end{itemize}

\section{Conclusion and User Intent}
The undersigned, Devin Phillip Davis (ADS-LLC), formally contests the originality and legality of the "Geometric Coherence" framework and all associated constants presented at ICGAC 2026. All evidence, Zenodo DOIs, and cryptographic hashes are provided for independent verification. The conference is hereby placed on notice of ongoing IP theft, legal liability, and the demand for immediate recognition of ADS-LLC's prior art and IP rights.

\end{document}
